\section{Scope and Limitations}
% This section identifies what part of the envisioned solution is going to be
% developed in this current project or version, what will be delayed until
% latter projects, and what is out of scope for the whole product.  
%
\subsection{Scope of Initial Release}
At the time of release PDF Grader will be able to take a set of scanned tests or worksheets and allow the user to select how they want to view the scans to grade. The user will be able to view the scans based on page numbers or parts of a page across all users at once or one test at a time. It will allow the user to mark each question with a grade, comments, or both and output the tests with these marks next to the question. Multiple users will be allowed to work on a set of scans at once and each add their own input for questions, provided they share a folder on a network. There will be assignable marks that can be assigned to hotkeys which will be changeable so that it affects the overall score differently than originally assigned.
\subsection{Scope of Subsequent Releases}
    Future releases will include different ways that the multiple graders will be able to access the documents. Handwriting recognition will be added so that the program can determine who the papers belong to for the users. Support for other operating systems besides Linux is planned.
\subsection{Limitations and Exclusions}
 There are no plans for this product to be integrated into online grading services. Once a user has graded something, they will have to manually input the given grades into their grade tracking software. Additionally, the program will be made for grading papers where the papers are the same length. It will be possible to grade an assignment where the papers of varying length but certain features may not work as well.
